Application of convolutional neural networks in optical text recognition to junk data filtering

### 2021-04-24 tex/paper/OMFI2021_Razumov_paper.tex
Minor changes
Minor changes in text around table 2 was added.

\begin {document}
\title{Application of convolutional neural networks in optical text recognition to junk data filtering}
\author{Razumov T.E.$^1$, Churikov D.V.$^2$, Kravchenko O.V.$^3$}

@@

The fully convolutional neural network with 3 layers was considered. A \textsf{ReLU} activation function was applied to the first and second layersthird, and the last one utilize \textsf{sigmoid} as an activation function. Data was regularized on each layer. Neural network can be defined as follows in our case
$$
g(x) = h_2 \left(\sum_{k=0}^{n_2} w''_k h_1\left(\sum_{j=0}^{n_1} w'_j h_0\left( \sum_{i=0}^{n_0} w_i x_i \right)\right)\right),
$$
where $h_i$ is the activation function for the corresponding layer. Adaptive moment estimation (Adam) method of gradient descent optimization algorithm is utilized to find weights $\{w_i\}$, $\{w'_j\}$, $\{w''_k\}$ at the model training stage.
The results for BOW and Fast Text embeddings with \textsf{ReLU},\,\textsf{sigmoid} activation function and Adam method are also introduced in table\,\ref{tbl:02}.

>>>>

\begin {document}
\title{Application of convolutional neural networks in optical text recognition to junk data filtering}
\author{Razumov T.E.$^1$, Churikov D.V.$^2$, Kravchenko O.V.$^{2,3}$}

@@

The fully convolutional neural network with 3 layers was considered. A \textsf{ReLU} activation function was applied to the first and second layersthird, and the last one utilize \textsf{sigmoid} as an activation function. Data was regularized on each layer. Neural network can be defined as follows in our case
$$
g(x) = h_2 \left(\sum_{k=0}^{n_2} w''_k h_1\left(\sum_{j=0}^{n_1} w'_j h_0\left( \sum_{i=0}^{n_0} w_i x_i \right)\right)\right),
$$
where $h_i$ is activation function for the corresponding layer. Adaptive moment estimation (Adam) method of gradient descent optimization algorithm is utilized to determine weights $\{w_i\}$, $\{w'_j\}$, $\{w''_k\}$ at the model training stage expet the last one.
The results for BOW and Fast Text embeddings FCNN model are also introduced in table\,\ref{tbl:02}.
